---
title: "RECIPES"
output: html_document
---

```{R}

install.packages("tidymodels") #fot hte recipies package and others functions
install.packages("skimr") # for variable summaries
library(skimr)
library(dplyr) #for data processing
library(here)
library(rsample)
library(recipes)
library(tidymodels)
```

```{r}
#path to data
data_location <-here::here("data","processed_data","newdata.rds")
dt<- readRDS(data_location)
```
```{r}
glimpse(dt)
```
#Split the data 
```{r}
# Put 3/4 of the data into the training set 
data_split <- initial_split(dt, prop = 3/4)

# Create data frames for the two sets:
train_data <- training(data_split)
test_data  <- testing(data_split)
```
## New recipe to fit the categorical outcome of interest (Nausea) to all predictors
```{r}
Nausea_rec<- 
  recipe(Nausea ~ ., data = train_data)

summary(Nausea_rec) #To get the current set of variables and role
```
```{r}
# Fit a logistic model 
lr_mod <- 
  logistic_reg() %>% 
  set_engine("glm")

# Model Workflow
Nausea_wflow <-
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(Nausea_rec)

# Preparing the recipe and train the model from the resulting predictors:
Nausea_fit<-
  Nausea_wflow %>%
  fit(data = train_data )

#Extracting the model coefficients
Nausea_fit %>%
   extract_fit_parsnip() %>% 
   tidy()
```
# Evaluating Model
# The ROC curve provides a graphical representation of a classifier’s performance
```{r}
predict(Nausea_fit, test_data )

#Predicting probabilities
Nausea_aug <-
  augment(Nausea_fit, test_data)

Nausea_aug %>%
  select(Nausea, .pred_class , .pred_No, .pred_Yes)

#ROC curve
Nausea_aug%>%
  roc_curve(truth = Nausea, .pred_No ) %>%
  autoplot()
# Getting the area under the curve
Nausea_aug%>%
  roc_auc(truth = Nausea, .pred_No )
```
#Since the ROC-AUC is 0.714 the model can considered acceptable.

#Alternative model: model that only fits the main predictor (RunnyNose) to the categorical outcome. 
```{r}
#New recipe for with Predictor = RunnyNose
Runnynose_rec<- 
  recipe(Nausea ~ RunnyNose, data = train_data)
```
```{r}

# Fit a logistic model 
lr_mod <- 
  logistic_reg() %>% 
  set_engine("glm")

# Model Workflow
Runnynose_wflow <-
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(Runnynose_rec)

# Preparing the recipe and train the model from the resulting predictors:
Runnynose_fit<-
  Runnynose_wflow %>%
  fit(data = train_data )

#Extracting the model coefficients
Runnynose_fit %>%
   extract_fit_parsnip() %>% 
   tidy()
```
#Evaluating Alternative Model
```{r}
predict(Runnynose_fit, test_data )

#Predicting probabilities
Runnynose_aug <-
  augment(Runnynose_fit, test_data)

#ROC curve
Runnynose_aug%>%
  roc_curve(truth = Nausea, .pred_No ) %>%
  autoplot()
# Getting the area under the curve
Runnynose_aug%>%
  roc_auc(truth = Nausea, .pred_No )
```
# Since the ROC-AUC is 0.504, we can conclude that the alternative model is not useful. 



  



        
