---
title: "Analysis"
output: html_document
---
```{r}
install.packages("tidymodels")
install.packages("tidyverse")
library(readxl) #for loading Excel files
library(dplyr) #for data processing
library(here) #to set paths
library(broom)
library(tidymodels)
```

#path to data and loading
#note the use of the here() package and not absolute paths
```{r}

data_location <-here::here("data","processed_data","newdata.rds")
expdata<- readRDS(data_location)
```
#It's time to MoDeLing!!!!!

#Fits a linear model to the continuous outcome using only the main predictor of interest. According with the exploration section ChillsSweats and WeaknessYN may are a good predictor for BodyTemp...

# Set the engine
```{r}
lm_mod <-  linear_reg() %>% set_engine("lm")
```
#Linear model BodyTemp ~ ChillsSweats 
```{r}
lm_bodyT<- lm(BodyTemp ~ ChillsSweats, data =expdata)
tidy(lm_bodyT)
```
#Fits another linear model to the continuous outcome using all (important) predictors of interest.
# Linear model BodyTemp ~ other predictors that I selected.
```{r}
lm_bodyT<- lm(BodyTemp ~ ChillsSweats + NasalCongestion +                 RunnyNose + WeaknessYN,  data =expdata)
tidy(lm_bodyT)
```




