---
title: "exploration"
output: html_document
---
This file is focus in exploring the data. It goes on `processing_code` in `code` file.

#load needed packages. make sure they are installed.
```{r}
install.packages("tidyverse")
library(readxl) #for loading Excel files
library(dplyr) #for data processing
library(here) #to set paths
library(tidyverse)
```

#path to data and loading
#note the use of the here() package and not absolute paths
```{r}
data_location <-here::here("data","processed_data","newdata.rds")
expdata<- readRDS(data_location)
```
#Looking the data
```{r}
glimpse(expdata)
```
#Outcomes:
#- Main continuous outcome of interest is Body temperature
#- Main categorical outcome is Nausea
```{r}
summary(expdata) 
```
#Categorical Analysis--> Nausea
#Categorical outcomes must be analysis with proportions 

```{r}
table1 <- table(expdata$Nausea)
prop.table(table1)%>% print()
```
65% of the population don't get Nausea and 35% get it.
#Plot for categorical outcome 
```{r}
nauceaplot <- ggplot(data = expdata) +
              geom_bar(mapping = aes(Nausea))
nauceaplot
#Save Plot 
saveRDS(nauceaplot, file = here("results", "nauceaplot.rds"))

```
#Continuos Analysis--> BodyTemp
```{r}
summary(expdata$BodyTemp)
```
```{r}
BodyT_plot<- ggplot(expdata, aes(x=BodyTemp)) + geom_histogram()
BodyT_plot
#Save Plot 
saveRDS(BodyT_plot, file = here("results", "BodyT_plot.rds"))
```
#Predictor variables 
#ChillsSweats, NasalCongestion, RunnyNose,
#WeaknessYN 

#BodyTemp and Nausea
```{r}
expdata %>% ggplot(aes(Nausea, BodyTemp) )+ geom_boxplot()
```
#BodyTemp and ChillsSweats
```{r}
expdata %>% ggplot(aes(ChillsSweats, BodyTemp) )+ geom_boxplot()
```
#BodyTemp and NasalCongestion
```{r}
expdata %>% ggplot(aes(NasalCongestion, BodyTemp) )+ geom_boxplot()                 
```
#BodyTemp and RunnyNose
```{r}
expdata %>% ggplot(aes(RunnyNose, BodyTemp) )+ geom_boxplot()                 
```
#BodyTemp and WeaknessYN
```{r}
summary(expdata$WeaknessYN)
expdata %>% ggplot(aes(WeaknessYN , BodyTemp) )+ geom_boxplot()                 
```
#Nacuea Vs. Predictors
#Nausea and ChillsSweats
```{r}
expdata %>% ggplot(aes(Nausea, ChillsSweats) )+ geom_count()
```

#Naucea and NasalCongestion
```{r}
expdata %>% ggplot(aes(Nausea, NasalCongestion) )+ geom_count()
```
#Naucea and RunnyNose
```{r}
expdata %>% ggplot(aes(Nausea, RunnyNose) )+ geom_count()
```
#Naucea and WeaknessYN
```{r}
expdata %>% ggplot(aes(Nausea, WeaknessYN ) )+ geom_count()
```
Based on the plot we can say that the Chills/Sweats and WeaknessYN may be can use as predictors of BodyTemp. Results were not clear for Nausea.

